---
title: "LAO MICS 3"
author: "Trude"
date: "06-05-2021"
output:
  html_document:
    toc: yes
    toc_depth: 3
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




# Lao PDR: MICS Data - mics3


I changed the structure of the file and delete some bits. If you want to see the earlier version, you can go to the git hub site and look at the previous version.



```{r options}

options(scipen = 999) # suppress scientific notion

```



```{r packages}

library(tidyverse)

# library(expss) # export

library(haven) 

library(sjPlot)

#library(sjlabelled)

#library(labelled)

#library(surveytoolbox) # install with #devtools::install_github("martinctc/surveytoolbox")

library(lubridate) # working with dates

library(survey)

library(srvyr)

#library(sjmisc)

#library(knitr)

library(janitor)

#library(survminer)

library(DataExplorer)

library(naniar)

```




## Data


```{r dataset mics3 ch}

mics3.ch <- read_sav("./data/mics3/ch.sav")


```


```{r dataset mics3 wm}

mics3.wm <- read_sav("./data/mics3/wm.sav")

```


```{r glimpse}

# Mothers or primary caretakers of children under five – ch.sav
dim(mics3.ch)
# [1] 4204 335 
glimpse(mics3.ch) 

# look at lables 
sjPlot::view_df(mics3.ch)
sjPlot::view_df(mics3.wm)

# Mother / caretaker
mics3.ch %>% count(UF6) # range from 1-16
# need to make a individual number for the merging

```



### Merging women data to children 


```{r merging}
# selecting subset of variables of women's dataset
mics3.wm_var <- subset(mics3.wm, select = c("HH1", "HH2", "LN", "MN2A", "MN2B", "MN2C", "MN2F", "MN2G", "MN2H", "MN2X", "MN2Y","MN8"))

# HH1-2, LN for identifying women
# MN2 - ANC
# MN8 - POB

# change variable name in women dataset in order to match with children's
# woman's line number instead of line number
mics3.wm_var$UF6 <- mics3.wm_var$LN
mics3.wm %>% count(LN, WM4) # probably the same variable


# Merge joining variables from dataset woman to dataset children_2017 using as key variable: UF4 (mothers or caretakers line number in ch.sav).
# Common variables used to merge are: HH1, HH2, UF4 in children, LN in women
mics3.ch_wm <- merge(mics3.ch, mics3.wm_var, by=c("HH1", "HH2", "UF6"), all.x = TRUE)

```


### New variables 


```{r household and child id}

# Household ID
mics3.ch_wm %>% unite(HH_id, c(HH1, HH2), sep = "_", remove = FALSE, na.rm = FALSE) -> mics3.ch_wm

# Are there any duplicates?
mics3.ch_wm %>% group_by(HH_id) %>% filter(n()>1) %>% summarize(n=n())
# 1046 duplicates meaning more children in one household

# Unique id for each child
# UF4 should be the individual number of each child (LN of child)

mics3.ch_wm %>% 
  unite(ch_id, 
        c(HH1, HH2, UF4), sep = "_", remove = FALSE, na.rm = FALSE) -> mics3.ch_wm
mics3.ch_wm %>% group_by(ch_id) %>% filter(n()>1) %>% summarize(n=n())
# none 

```


```{r strata}

# strata
# Do I need a new variable combining HH6 and HH7?

# The sample for the Lao PDR Multiple Indicator Cluster Survey (MICS) was designed to provide estimates on a large number of indicators conerning the situation of children and women at the national level, for urban and rural areas, and for three regions: North, Central and South.

mics3.ch_wm %>% 
  unite(strata, c(HH7, HH6), sep = "_", remove = FALSE, na.rm = FALSE) -> mics3.ch_wm
mics3.ch_wm %>% count(strata)

```



```{r date of interview}

# Day of the interview

mics3.ch_wm$UF8D_2 <- as.numeric(as.character(mics3.ch_wm$UF8D))
mics3.ch_wm$UF8Y_2 <- as.numeric(as.character(mics3.ch_wm$UF8Y))
mics3.ch_wm$UF8M_2 <- as.numeric(as.character(mics3.ch_wm$UF8M))

# day of interview
mics3.ch_wm %>%  mutate(I_date = make_date(UF8Y_2, UF8M_2, UF8D_2)) -> mics3.ch_wm
# A function from lubridate package

```



```{r date of birth}

# Date of birth 
mics3.ch_wm %>% count(UF10D)
mics3.ch_wm %>% count(UF10M)

class(mics3.ch_wm$UF10M)

mics3.ch_wm$UF10D_2 <- as.numeric(mics3.ch_wm$UF10D)

mics3.ch_wm$UF10M_2 <- as.numeric(mics3.ch_wm$UF10M)

mics3.ch_wm$UF10Y_2 <- as.numeric(mics3.ch_wm$UF10Y)

mics3.ch_wm %>%  mutate(dob_ch = make_date(UF10Y_2, UF10M_2, UF10D_2)) -> mics3.ch_wm

```



### Subset



The data will be subset into children from 1 to 2 years of age for the analysis of the hepatitis B vaccinations.


```{r mics3.ch_p1}

mics3.ch_wm %>% filter(UF11 >= 1) -> mics3.ch_p1


```



## mics3.ch_p1


### Variables


#### tetravalent vaccine


```{r tetravalent 1}



# tetra 1 Only Card

mics3.ch_p1 %>% count(IM5AD)

#change date variables into categorical variables
mics3.ch_p1 %>% mutate(tetra1_C = if_else(IM5AD <= 31 & IM5AD >=1, 1,
                                        if_else(IM5AD == 0, 0,
                                        if_else(IM5AD == 44, 44, 66)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra1_C)

mics3.ch_p1 %>% 
  mutate(tetra1_C = recode(tetra1_C,
                           "44" = "1",
                           "66" = "66",
                           "1" = "1",
                           "0" = "0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra1_C)

# 66 needs to be replaced with NA because this is recall info and not card info # not neccesary here because there are no entries with 66

mics3.ch_p1$tetra1_C_1 <- mics3.ch_p1$tetra1_C
mics3.ch_p1 %>% replace_with_na(replace = list(tetra1_C_1 = "66")) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra1_C_1) # 0: 394 1: 324




```



```{r tetravalent 2}



# tetra 2 Only Card

mics3.ch_p1 %>% count(IM5BD)

#change date variables into categorical variables
mics3.ch_p1 %>% mutate(tetra2_C = if_else(IM5BD <= 31 & IM5BD >=1, 1,
                                        if_else(IM5BD == 0, 0,
                                        if_else(IM5BD == 44, 44, 66)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra2_C)

mics3.ch_p1 %>% 
  mutate(tetra2_C = recode(tetra2_C,
                           "44" = "1",
                           "66" = "66",
                           "1" = "1",
                           "0" = "0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra2_C)

# 66 needs to be replaced with NA because this is recall info and not card info

mics3.ch_p1$tetra2_C_1 <- mics3.ch_p1$tetra2_C
mics3.ch_p1 %>% replace_with_na(replace = list(tetra2_C_1 = "66")) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra2_C_1) # 0: 419 1: 298



```



```{r tetravalent 3}


# tetra 3 Only Card

mics3.ch_p1 %>% count(IM5CD)

#change date variables into categorical variables
mics3.ch_p1 %>% mutate(tetra3_C = if_else(IM5CD <= 31 & IM5CD >=1, 1,
                                        if_else(IM5CD == 0, 0,
                                        if_else(IM5CD == 44, 44, 66)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra3_C)

mics3.ch_p1 %>% 
  mutate(tetra3_C = recode(tetra3_C,
                           "44" = "1",
                           "66" = "66",
                           "1" = "1",
                           "0" = "0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra3_C)

# 66 needs to be replaced with NA because this is recall info and not card info

mics3.ch_p1$tetra3_C_1 <- mics3.ch_p1$tetra3_C
mics3.ch_p1 %>% replace_with_na(replace = list(tetra3_C_1 = "66")) -> mics3.ch_p1
mics3.ch_p1 %>% count(tetra3_C_1) # 0: 474 1: 238



```




#### DPT vaccine


```{r DTP 1}

# DPT 1 Only Card

mics3.ch_p1 %>% count(IM4AD)

#change date variables into categorical variables
mics3.ch_p1 %>% mutate(DPT1_C = if_else(IM4AD <= 31 & IM4AD >=1, 1,
                                        if_else(IM4AD == 0, 0,
                                        if_else(IM4AD == 44, 44, 66)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_C)
mics3.ch_p1 %>% count(DPT1_C, IM15)
mics3.ch_p1 %>% count(DPT1_C, IM15, IM10, IM9)


mics3.ch_p1 %>% 
  mutate(DPT1_C = recode(DPT1_C,
                           "44" = "1",
                           "66" = "66",
                           "1" = "1",
                           "0" = "0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_C)

# 66 needs to be replaced with NA because this is recall info and not card info # not neccesary here because there are no entries with 66

mics3.ch_p1$DPT1_C_1 <- mics3.ch_p1$DPT1_C
mics3.ch_p1 %>% replace_with_na(replace = list(DPT1_C_1 = "66")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_C_1)


# DTP1 only recall

mics3.ch_p1 %>% count(IM9, IM10, IM15, DPT1_C_1)
mics3.ch_p1 %>% count(IM9, DPT1_C_1)
mics3.ch_p1 %>% count(IM10, IM15)



# First recode IM15 into DPT1_R: recall variable

mics3.ch_p1 %>% count(IM15)
mics3.ch_p1 %>% 
  mutate(DPT1_R = recode(IM15,
                           "1" = "R_1",
                           "2" = "R_0",
                           "8" = "R_8",
                           "9" = "R_9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_R)



# It is not yet correct
# In IM10; if all responses were "NO"; there was no probing for the recall of vaccinations
# Therefore; some of the NAs in the new variable need to be changed to "No" or "DK" #512 no and #13 DK and 2 No response

mics3.ch_p1 %>% 
  mutate(DPT1_R = replace(DPT1_R, is.na(DPT1_R) & IM10 == 2, "R_0"))  %>%
  mutate(DPT1_R = replace(DPT1_R, is.na(DPT1_R) & IM10 == 8, "R_8")) %>%
  mutate(DPT1_R = replace(DPT1_R, is.na(DPT1_R) & IM10 == 9, "R_9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_R)


# combine Recall and Card

mics3.ch_p1 %>% count(DPT1_R, DPT1_C)
mics3.ch_p1 %>% mutate(DPT1_RC = coalesce(DPT1_C, DPT1_R)) -> mics3.ch_p1 
mics3.ch_p1 %>% count(DPT1_RC, IM9)

# Only 1 response is still NA, not categorized. This is solved when using IM9, then the category is 2: Missing, so this response will be categorized as R_0.

mics3.ch_p1 %>% 
  mutate(DPT1_RC = replace(DPT1_RC, is.na(DPT1_RC) & IM9 == 2, "R_0")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_RC)


mics3.ch_p1 %>% 
  mutate(DPT1_R_1 = recode(DPT1_RC,
                           "R_0" = "R_0",
                           "R_1" = "R_1",
                           "R_8" = "R_0",
                           "R_9" = "R_0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_R_1)

# all outcomes from card RC need to be replaced with NA to only retain recall
mics3.ch_p1 %>% replace_with_na(replace = list(DPT1_R_1 = c("0", "1"))) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT1_R_1)

# combination recall and card
mics3.ch_p1 %>%
  mutate(DPT1_RC_1 = recode(DPT1_RC,
                              "0" = 0,
                              "1" = 1,
                              "R_9" = 0,
                              "R_0" = 0,
                              "R_1" = 1,
                              "R_8" = 0
                              )) -> mics3.ch_p1

mics3.ch_p1 %>% count(DPT1_RC_1) # 0: 592 1: 1064
mics3.ch_p1 %>% count(DPT1_R_1) # 0: 583 1: 355
mics3.ch_p1 %>% count(DPT1_C_1) # 0: 9 1: 709

mics3.ch_p1 %>% count(DPT1_C, tetra1_C)


```



```{r DTP 2}

# DPT 2 Only Card

mics3.ch_p1 %>% count(IM4BD)

#change date variables into categorical variables
mics3.ch_p1 %>% mutate(DPT2_C = if_else(IM4BD <= 31 & IM4BD >=1, 1,
                                        if_else(IM4BD == 0, 0,
                                        if_else(IM4BD == 44, 44, 66)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_C)
mics3.ch_p1 %>% count(DPT2_C, IM15)
mics3.ch_p1 %>% count(DPT2_C, IM15, IM10, IM9)


mics3.ch_p1 %>% 
  mutate(DPT2_C = recode(DPT2_C,
                           "44" = "1",
                           "66" = "66",
                           "1" = "1",
                           "0" = "0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_C)

# 66 needs to be replaced with NA because this is recall info and not card info # not neccesary here because there are no entries with 66

mics3.ch_p1$DPT2_C_1 <- mics3.ch_p1$DPT2_C
mics3.ch_p1 %>% replace_with_na(replace = list(DPT2_C_1 = "66")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_C_1)


# DTP1 only recall

mics3.ch_p1 %>% count(IM9, IM10, IM15, DPT2_C_1)
mics3.ch_p1 %>% count(IM9, DPT2_C_1)
mics3.ch_p1 %>% count(IM10, IM15)



# First recode IM15 into DPT2_R: recall variable

mics3.ch_p1 %>% count(IM15)
mics3.ch_p1 %>% 
  mutate(DPT2_R = recode(IM15,
                           "1" = "R_1",
                           "2" = "R_0",
                           "8" = "R_8",
                           "9" = "R_9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_R)

# Then recode IM16 into DPT2_R_2: recall variable

mics3.ch_p1 %>% count(IM16)
mics3.ch_p1 %>% 
  mutate(DPT2_R_2 = recode(IM16,
                           "1" = "R_1",
                           "2" = "R_2",
                           "3" = "R_3",
                           "4" = "R_4",
                           "5" = "R_5",
                           "6" = "R_6",
                           "7" = "R_7",
                           "8" = "R_8",
                           "9" = "R_9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_R_2)

# make a new variable combining IM15 and IM16. 
# IM 21: 2,3,4,5,6 of 7 means having the second DPT vaccine, IM16: 1,8 or 9 had only one or dont know whether they had one DPT vaccine or more, therefore do not include them assign to 0 together with IM15 No and DK.
 
mics3.ch_p1 %>% count(DPT2_R_2, DPT1_R)
mics3.ch_p1 %>% mutate(DPT2_R_3 = coalesce(DPT2_R_2, DPT1_R)) -> mics3.ch_p1 
mics3.ch_p1 %>% count(DPT2_R_3)

mics3.ch_p1 %>% count(IM9, IM10, DPT2_R_3) # everything is correct, no need for replacing

# Recode recall variable DPT2 into yes or no

mics3.ch_p1 %>% 
  mutate(DPT2_R_2 = recode(DPT2_R_3,
                           "R_0" = "R_0",
                           "R_1" = "R_0",
                           "R_2" = "R_1",
                           "R_3" = "R_1",
                           "R_4" = "R_1",
                           "R_5" = "R_1",
                           "R_6" = "R_1",
                           "R_7" = "R_1",
                           "R_8" = "R_0",
                           "R_9" = "R_0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_R_2)


# combine Recall and Card

mics3.ch_p1 %>% count(DPT2_R_2, DPT2_C)

# R_0	0	  3		
# R_0	1	  21		
# R_0	NA	663		
# R_1	1	  10		
# R_1	NA	274		
# NA	0	  71		
# NA	1	  606		
# NA	NA	8

# 21 children have 1 on card and value 0 on recall; 1o children have value 1 on card and 1 on recall, 8 children have no value on both card. 
# 21 and 10 children should be counted on the card, in recall variable change for NA

mics3.ch_p1 %>% mutate(DPT2_RC = coalesce(DPT2_C, DPT2_R_2)) -> mics3.ch_p1 
mics3.ch_p1 %>% count(DPT2_RC, IM9)

# Only 1 response is still NA, not categorized. This is solved when using IM9, then the category is 2: Missing, so this response will be categorized as R_0.

mics3.ch_p1 %>% 
  mutate(DPT2_RC = replace(DPT2_RC, is.na(DPT2_RC) & IM9 == 2, "R_0")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_RC)
mics3.ch_p1 %>% 
  mutate(DPT2_RC = replace(DPT2_RC, is.na(DPT2_RC) & IM9 == 1, "R_0")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_RC)


mics3.ch_p1 %>% 
  mutate(DPT2_R_1 = recode(DPT2_RC,
                           "R_0" = "R_0",
                           "R_1" = "R_1",
                           "R_8" = "R_0",
                           "R_9" = "R_0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_R_1)

# all outcomes from card RC need to be replaced with NA to only retain recall
mics3.ch_p1 %>% replace_with_na(replace = list(DPT2_R_1 = c("0", "1"))) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT2_R_1)

# combination recall and card
mics3.ch_p1 %>%
  mutate(DPT2_RC_1 = recode(DPT2_RC,
                              "0" = 0,
                              "1" = 1,
                              "R_9" = 0,
                              "R_0" = 0,
                              "R_1" = 1,
                              "R_8" = 0
                              )) -> mics3.ch_p1

mics3.ch_p1 %>% count(DPT2_RC_1) # 0: 745 1: 911
mics3.ch_p1 %>% count(DPT2_R_1) # 0: 671 1: 274
mics3.ch_p1 %>% count(DPT2_C_1) # 0: 74 1: 637




```





```{r DTP 3}

# DPT 2 Only Card

mics3.ch_p1 %>% count(IM4CD)

#change date variables into categorical variables
mics3.ch_p1 %>% mutate(DPT3_C = if_else(IM4CD <= 31 & IM4CD >=1, 1,
                                        if_else(IM4CD == 0, 0,
                                        if_else(IM4CD == 44, 44, 66)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_C)
mics3.ch_p1 %>% count(DPT3_C, IM15)
mics3.ch_p1 %>% count(DPT3_C, IM15, IM10, IM9)


mics3.ch_p1 %>% 
  mutate(DPT3_C = recode(DPT3_C,
                           "44" = "1",
                           "66" = "66",
                           "1" = "1",
                           "0" = "0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_C)

# 66 needs to be replaced with NA because this is recall info and not card info # not neccesary here because there are no entries with 66

mics3.ch_p1$DPT3_C_1 <- mics3.ch_p1$DPT3_C
mics3.ch_p1 %>% replace_with_na(replace = list(DPT3_C_1 = "66")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_C_1)


# DTP1 only recall

mics3.ch_p1 %>% count(IM9, IM10, IM15, DPT3_C_1)
mics3.ch_p1 %>% count(IM9, DPT3_C_1)
mics3.ch_p1 %>% count(IM10, IM15)



# First recode IM15 into DPT3_R: recall variable

mics3.ch_p1 %>% count(IM15)
mics3.ch_p1 %>% 
  mutate(DPT3_R = recode(IM15,
                           "1" = "R_1",
                           "2" = "R_0",
                           "8" = "R_8",
                           "9" = "R_9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_R)

# Then recode IM16 into DPT3_R_2: recall variable

mics3.ch_p1 %>% count(IM16)
mics3.ch_p1 %>% 
  mutate(DPT3_R_2 = recode(IM16,
                           "1" = "R_1",
                           "2" = "R_2",
                           "3" = "R_3",
                           "4" = "R_4",
                           "5" = "R_5",
                           "6" = "R_6",
                           "7" = "R_7",
                           "8" = "R_8",
                           "9" = "R_9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_R_2)

# make a new variable combining IM15 and IM16. 
# IM 21: 2,3,4,5,6 of 7 means having the second DPT vaccine, IM16: 1,8 or 9 had only one or dont know whether they had one DPT vaccine or more, therefore do not include them assign to 0 together with IM15 No and DK.
 
mics3.ch_p1 %>% count(DPT3_R_2, DPT1_R)
mics3.ch_p1 %>% mutate(DPT3_R_3 = coalesce(DPT3_R_2, DPT1_R)) -> mics3.ch_p1 
mics3.ch_p1 %>% count(DPT3_R_3)

mics3.ch_p1 %>% count(IM9, IM10, DPT3_R_3) # everything is correct, no need for replacing

# Recode recall variable DPT3 into yes or no

mics3.ch_p1 %>% 
  mutate(DPT3_R_2 = recode(DPT3_R_3,
                           "R_0" = "R_0",
                           "R_1" = "R_0",
                           "R_2" = "R_0",
                           "R_3" = "R_1",
                           "R_4" = "R_1",
                           "R_5" = "R_1",
                           "R_6" = "R_1",
                           "R_7" = "R_1",
                           "R_8" = "R_0",
                           "R_9" = "R_0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_R_2)


# combine Recall and Card

mics3.ch_p1 %>% count(DPT3_R_2, DPT3_C)

# R_0	0	  3		
# R_0	1	  21		
# R_0	NA	663		
# R_1	1	  10		
# R_1	NA	274		
# NA	0	  71		
# NA	1	  606		
# NA	NA	8

# 21 children have 1 on card and value 0 on recall; 1o children have value 1 on card and 1 on recall, 8 children have no value on both card. 
# 21 and 10 children should be counted on the card, in recall variable change for NA

mics3.ch_p1 %>% mutate(DPT3_RC = coalesce(DPT3_C, DPT3_R_2)) -> mics3.ch_p1 
mics3.ch_p1 %>% count(DPT3_RC, IM9)

# Only 1 response is still NA, not categorized. This is solved when using IM9, then the category is 2: Missing, so this response will be categorized as R_0.

mics3.ch_p1 %>% 
  mutate(DPT3_RC = replace(DPT3_RC, is.na(DPT3_RC) & IM9 == 2, "R_0")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_RC)
mics3.ch_p1 %>% 
  mutate(DPT3_RC = replace(DPT3_RC, is.na(DPT3_RC) & IM9 == 1, "R_0")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_RC)
mics3.ch_p1 %>% 
  mutate(DPT3_RC = replace(DPT3_RC, is.na(DPT3_RC) & IM9 == 8, "R_0")) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_RC)


mics3.ch_p1 %>% 
  mutate(DPT3_R_1 = recode(DPT3_RC,
                           "R_0" = "R_0",
                           "R_1" = "R_1",
                           "R_8" = "R_0",
                           "R_9" = "R_0"
                           )) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_R_1)

# all outcomes from card RC need to be replaced with NA to only retain recall
mics3.ch_p1 %>% replace_with_na(replace = list(DPT3_R_1 = c("0", "1"))) -> mics3.ch_p1
mics3.ch_p1 %>% count(DPT3_R_1)

# combination recall and card
mics3.ch_p1 %>%
  mutate(DPT3_RC_1 = recode(DPT3_RC,
                              "0" = 0,
                              "1" = 1,
                              "R_9" = 0,
                              "R_0" = 0,
                              "R_1" = 1,
                              "R_8" = 0
                              )) -> mics3.ch_p1

mics3.ch_p1 %>% count(DPT3_RC_1) # 0: 962 1: 694
mics3.ch_p1 %>% count(DPT3_R_1) # 0: 793 1: 173
mics3.ch_p1 %>% count(DPT3_C_1) # 0: 169 1: 521

```

```{r penta 123}

# check if they got all 3 vaccinations, not only second or third. 


mics3.ch_p1 %>% count(DPT1_RC_1, DPT2_RC_1, DPT3_RC_1)


# new variables at least one vaccine


# new variable penta1 got at least one vaccinations according to card or recall
mics3.ch_p1 %>% mutate(penta1_RC = if_else(DPT1_RC_1 == 1 | DPT2_RC_1 == 1 | DPT3_RC_1 == 1, 1, 0)) -> mics3.ch_p1
mics3.ch_p1 %>% count(penta1_RC)



# new variable penta12 got at least two vaccinations according to card or recall
mics3.ch_p1 %>% mutate(penta12_RC = if_else(DPT1_RC_1 == 1 & DPT2_RC_1 == 1, 1,
                                    if_else(DPT1_RC_1 == 1 & DPT3_RC_1 == 1, 1,
                                    if_else(DPT2_RC_1 == 1 & DPT3_RC_1 == 1, 1, 0)))) -> mics3.ch_p1
mics3.ch_p1 %>% count(penta12_RC)


# new variable penta123 got at least three vaccinations according to card or recall
mics3.ch_p1 %>% mutate(penta123_RC = if_else(DPT1_RC_1 == 1 & DPT2_RC_1 == 1 & DPT3_RC_1 == 1, 1, 0)) -> mics3.ch_p1
mics3.ch_p1 %>% count(penta123_RC)





```

#### Antenatal care

```{r anc}
mics3.ch_p1 %>% count(IM5AD, IM4AD, tetra1_C, DPT1_C)

# new variable place of delivery
mics3.ch_p1 %>% 
  mutate(MN8_1 = recode(MN8,
                        "11" = "1",
                        "12" = "1",
                        "21" = "2",
                        "22" = "2",
                        "26" = "2",
                        "31" = "3",
                        "32" = "3",
                        "33" = "3",
                        "36" = "3",
                        "96" = "9",
                        "98" = "9",
                        "99" = "9")) -> mics3.ch_p1
mics3.ch_p1 %>% count(MN8, MN8_1)

```




### Survey design


```{r survey design}

# The sample for the Lao PDR Multiple Indicator Cluster Survey (MICS) was designed to provide estimates on a large number of indicators conerning the situation of children and women at the national level, for urban and rural areas, and for three regions: North, Central and South. Regions were identified as the main sampling domains and the sample was selected in two stages. Within each region, 100 census enumeration areas were selected with probability proportional to size. After a household listing was carried out within the selected enumeration areas, a systematic sample of 20 households was drawn. Although the sample was designed to collect information from 6,000 households, it was known in advance that one village only had 15 households, therefore the total expected number of households was 5,995. Of the selected enumeration areas, all but two were visited during the fieldwork period. The two missing enumeration areas were replaced in the field with villages of similar area type. The sample was stratified by region and is not self-weighting. For reporting national level results, sample weights are used. A more detailed description of the sample design can be found in Appendix A.



# Understanding the sample design
mics3.ch_wm %>% count(HH1) # enumeration areas; 20 hh were drawn for each enumeration area
mics3.ch_wm %>% count(HH6) # Area
mics3.ch_wm %>% tabyl(HH7, HH6)

mics3.ch_wm %>% count(strata) # 9 rows



# Make design for pentavalent with selected children aged under 3 and older than 1 year: n = 1656

mics_design_p1 <- svydesign(data = mics3.ch_p1, 
                         weights = ~chweight, 
                         id = ~strata+HH1)



```



### Descriptive analysis - weighted


#### Independent variables

```{r descriptive}


# taking survey design into account 

# What are interesting things to explore in the dataset?

# Province
# Area
# Direction?
# Wealth score
# melevel education mother
# Age
# Ethnicity

tab_ethnicity <- svytable(~HC1C, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_ethnicity

# For comparison:

mics3.ch_p1 %>% 
  as_survey(weights = c(chweight)) %>% 
  group_by(HC1C) %>% 
  summarize(n = survey_total()) # same result


tab_melevel <- svytable(~melevel, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_melevel 
  
tab_HL4 <- svytable(~HL4, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_HL4 

tab_windex5 <- svytable(~wlthind5, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_windex5 

tab_HH6 <- svytable(~HH6, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_HH6 

tab_HH7 <- svytable(~HH7, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_HH7 

 
# combination of independent variables in graphs

svytable(~HC1C + HH7, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=HC1C, y=Freq, fill = HH7)) +
  geom_col(position = "fill") +
  coord_flip()


svytable(~HC1C + wlthind5, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=HC1C, y=Freq, fill = wlthind5)) +
  geom_col(position = "fill") +
  coord_flip()


svytable(~melevel + HH6, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=melevel, y=Freq, fill = HH6)) +
  geom_col(position = "fill") +
  coord_flip()


svytable(~melevel + HH7, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=melevel, y=Freq, fill = HH7)) +
  geom_col(position = "fill") +
  coord_flip()


svytable(~melevel + wlthind5, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=melevel, y=Freq, fill = wlthind5)) +
  geom_col(position = "fill") +
  coord_flip()



# Age should not give too many surprises?
svytable(~UF11 + HH7, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=UF11, y=Freq, fill = HH7)) +
  geom_col(position = "fill") +
  coord_flip()

svytable(~HC1C + UF11, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=HC1C, y=Freq, fill = UF11)) +
  geom_col(position = "fill") +
  coord_flip()

svytable(~HL4 + UF11, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
ggplot(data = tab, mapping = aes(x=HL4, y=Freq, fill = UF11)) +
  geom_col(position = "fill") +
  coord_flip()


```



```{r anc}

# place of delivery: MN8
mics3.ch_p1 %>% count(MN8_1)
tab_MN8 <- svytable(~MN8_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN8 


# antenatal care provider
mics3.ch_p1 %>% count(MN2A, MN2B, MN2C,MN2F, MN2G, MN2H, MN2X, MN2Y)

tab_MN2A <- svytable(~MN2A, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2A 
tab_MN2B <- svytable(~MN2B, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2B
tab_MN2C <- svytable(~MN2C, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2C
tab_MN2F <- svytable(~MN2F, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2F
tab_MN2G <- svytable(~MN2G, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2G
tab_MN2H <- svytable(~MN2H, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2H
tab_MN2X <- svytable(~MN2X, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2X
tab_MN2Y <- svytable(~MN2Y, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_MN2Y

```


```{r descriptive - dependent variables}

tab_tetra1_C_1 <- svytable(~tetra1_C_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_tetra1_C_1 

tab_tetra2_C_1 <- svytable(~tetra2_C_1, design = mics_design_p1) %>% 
 as.data.frame() %>% 
 mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
 mutate(Total = sum(Freq)) 
tab_tetra2_C_1 

tab_tetra3_C_1 <- svytable(~tetra3_C_1, design = mics_design_p1) %>% 
 as.data.frame() %>% 
 mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
 mutate(Total = sum(Freq)) 
tab_tetra3_C_1 


tab_DPT1_RC_1 <- svytable(~DPT1_RC_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT1_RC_1 

tab_DPT1_R_1 <- svytable(~DPT1_R_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT1_R_1 

tab_DPT1_C_1 <- svytable(~DPT1_C_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT1_C_1 

tab_DPT2_RC_1 <- svytable(~DPT2_RC_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT2_RC_1 

tab_DPT2_R_1 <- svytable(~DPT2_R_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT2_R_1 

tab_DPT2_C_1 <- svytable(~DPT2_C_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT2_C_1 

tab_DPT3_RC_1 <- svytable(~DPT3_RC_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT3_RC_1 

tab_DPT3_R_1 <- svytable(~DPT3_R_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT3_R_1 

tab_DPT3_C_1 <- svytable(~DPT3_C_1, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab_DPT3_C_1 

tab <- svytable(~penta1_RC, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab 

tab <- svytable(~penta12_RC, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab 

tab <- svytable(~penta123_RC, design = mics_design_p1) %>% 
  as.data.frame() %>% 
  mutate(Prop = round(Freq / sum(Freq)*100, 2)) %>%
  mutate(Total = sum(Freq)) 
tab 

```



#### Bivariate analysis


```{r inference}

# Looking at two variables: Ethnicity and area (urban / rural)
# Is there an association?

# survey design 

svytable(~HC1C + HH6, design = mics_design_p1) -> tab
tab <- as.data.frame(tab)
tab
ggplot(data = tab, mapping = aes(x=HC1C, y=Freq, fill = HH6)) +
  geom_col(position = "fill") +
  coord_flip()


# H0: Area not associated with race
# H1: Area associated with race
# svychisq(~HC1C + HH6, design = mics_design, statistic = "Chisq") 


svychisq(~HC1C + HH6, design = mics_design_p1, statistic = "Chisq") 
# X-squared = 363.71, df = 8, p-value = 0.7144





# Getting summary statistics while accounting for survey design

# what would be a numeric variable??
# UF11
svymean(~UF11, design = mics_design_p1, na.rm=TRUE)
#       mean     SE
# UF11 2.0415 0.016

svyquantile(x = ~UF11, design = mics_design_p1, na.rm=TRUE, quantiles = 0.5) # 2



```


